Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

Type theory is another formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
By following the Curry-Howard correspondence, we say
\emph{types} are theorems and their \emph{terms} are their proofs.

@@

\begin{notation}
Types are written using small caps.
We write the type judgments as $m : \abbre{M}$ to denote
that $m$ has $\abbre{M}$ type.
\end{notation}

>>>>

Type theory is another formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
It was proposed in 1902 to avoid the Russell's paradox and it follows
the same philosophy of constructive mathematics where the witness of
a statement is \emph{everything}. In that direction, we could say
the main actors in type theory are the statements and their proofs.
By following the Curry-Howard correspondence (see, for example,~\cite{Wadler-2015}), we say
\emph{types} are theorems and their \emph{terms} are their proofs.

@@

\begin{notation}
  Types are written using \abbre{small caps}.  We write the type
  judgments as $m : \abbre{m}$ to denote that~$m$ is of
  type~$\abbre{m}$.
\end{notation}
